---
title: "Quality Control"
author: CSDAV
output:
  beamer_presentation:
    toc: true
    slide_level: 3
    dev: png
fontsize: 8pt
theme: "Frankfurt"
highlight: tango
params:
  annotation: 0
  annotation1: 0
  counts: 0
  sgRNA_log_reps: 0
  sgRNA_lfc_reps: 0
  sgRNA_lfc: 0
  gene_lfc_reps: 0
  gene_lfc: 0
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,eval=FALSE,message=FALSE,warning=FALSE,results='hide')
source("../R/plotting.R")
```

```{r input,eval=TRUE}
annotation <- params$annotation
annotation1 <- params$annotation1

# pseudo <- params$pseudo
# weights <- params$weights
# scaling <- params$scaling
# shifting <- params$shifting

counts <- params$counts
logged <- params$sgRNA_log_reps
sgRNA_reps <- params$sgRNA_lfc_reps
sgRNA <- params$sgRNA_lfc
gene_reps <- params$gene_lfc_reps
gene <- params$gene_lfc

if(!"Category"%in%colnames(counts))
  counts$Category <- logged$Category <- sgRNA_reps$Category <- sgRNA$Category <- gene_reps$Category <- gene$Category <- "All"

library <- counts[,c("sgRNA","Gene","Category")]
counts_mat <- as.matrix(counts[,sapply(counts,is.numeric),drop=FALSE])
rownames(counts_mat) <- counts$sgRNA
logged_mat <- as.matrix(logged[,sapply(logged,is.numeric),drop=FALSE])
rownames(logged_mat) <- logged$sgRNA
sgRNA_reps_mat <- as.matrix(sgRNA_reps[,sapply(sgRNA_reps,is.numeric),drop=FALSE])
rownames(sgRNA_reps_mat) <- sgRNA_reps$sgRNA
sgRNA_mat <- as.matrix(sgRNA[,sapply(sgRNA,is.numeric),drop=FALSE])
rownames(sgRNA_mat) <- sgRNA$sgRNA
gene_reps_mat <- as.matrix(gene_reps[,sapply(gene_reps,is.numeric),drop=FALSE])
rownames(gene_reps_mat) <- gene_reps$Gene
gene_mat <- as.matrix(gene[,sapply(gene,is.numeric),drop=FALSE])
rownames(gene_mat) <- gene$Gene
```

# Read counts

### Number of core essentials / nonessentials
```{r classification,eval=TRUE}
plot.classification(library,counts_mat)
```

### Gene sizes
```{r sizes,eval=TRUE}
plot.sizes(library, counts_mat)
```

### Sequencing depth
```{r depths,eval=TRUE}
plot.depths(counts)
```

### Zero counts per category
```{r zeros,eval=TRUE}
plot.zeros(counts)
```

<!-- ### Cumulative distributions -->
```{r cumulative,eval=FALSE}
plot.cumulative(counts_mat, annotation)
```

<!-- # Normalized counts -->

<!-- ### Pseudocount optimization -->
```{r pseudocount,eval=FALSE}
if(!is.null(pseudo)) plot.pseudocount(pseudo)
```

<!-- ### Preliminary sgRNA rank weights from unfiltered controls -->
```{r weights,eval=FALSE}
plot.weights(weights)
```

<!-- ### Preliminary sgRNA sample scaling factors from unfiltered controls -->
```{r scaling,eval=FALSE}
plot.scaling(scaling)
```

<!-- ### Preliminary sgRNA sample shifting factors from unfiltered controls -->
```{r shifting,eval=FALSE}
plot.shifting(shifting)
```

### Distributions
```{r distributions,eval=TRUE}
plot.distributions(logged, annotation, "Condition~Replicate")
```

# Correlations and PCA

### sgRNA Pearson correlations
```{r sgRNA_correlations,eval=TRUE}
if(ncol(sgRNA_reps_mat)>1) plot.correlation(sgRNA_reps_mat)
```

### Gene Pearson correlations
```{r gene_correlations,eval=TRUE}
if(ncol(gene_reps_mat)>1) plot.correlation(gene_reps_mat)
```

### sgRNA Principal component analysis
```{r pca1,eval=TRUE}
if(ncol(sgRNA_reps_mat)>2) {
  tmp1 <- sgRNA_reps_mat
  pca_sample <- stats::prcomp(t(tmp1),scale=F)
  pca <- data.frame(Z1=pca_sample$x[,1],Z2=pca_sample$x[,2],Z3=pca_sample$x[,3],Sample=colnames(tmp1))
  plot.pca(pca)
}
```

### Gene Principal component analysis
```{r pca2,eval=TRUE}
if(ncol(gene_reps_mat)>2) {
  tmp1 <- gene_reps_mat
  pca_sample <- stats::prcomp(t(tmp1),scale=F)
  pca <- data.frame(Z1=pca_sample$x[,1],Z2=pca_sample$x[,2],Z3=pca_sample$x[,3],Sample=colnames(tmp1))
  plot.pca(pca)
}
```

### Proportion of variance explained
```{r pve,eval=TRUE}
if(ncol(gene_reps_mat)>2) {
  pve_sample <- 100*pca_sample$sdev^2/sum(pca_sample$sdev^2)
  plot.pve(pve_sample)
}
```

### sgRNA reproducibility in first condition
```{r reproducibility_sgRNA,eval=TRUE}
if(ncol(sgRNA_reps_mat)>1) {
  conditions <- unique(annotation1$Condition)
  annotation2 <- annotation1[annotation1$Condition==conditions[1],]
  grp <- split(annotation2$Sample,annotation2[c("Condition")],drop=TRUE)
  plot.reproducibility(sgRNA_reps[,c("Category",as.character(grp[[1]]))],names(grp)[1])
}
```

### Gene reproducibility in first condition
```{r reproducibility_gene,eval=TRUE}
if(ncol(gene_reps_mat)>1) {
  conditions <- unique(annotation1$Condition)
  annotation2 <- annotation1[annotation1$Condition==conditions[1],]
  grp <- split(annotation2$Sample,annotation2[c("Condition")],drop=TRUE)
  plot.reproducibility(gene_reps[,c("Category",as.character(grp[[1]]))],names(grp)[1])
}
```

### sgRNA reproducibility in second condition
```{r reproducibility_3,eval=TRUE}
if(ncol(sgRNA_reps_mat)>1) {
  annotation2 <- annotation1[annotation1$Condition==conditions[2],]
  grp <- split(annotation2$Sample,annotation2[c("Condition")],drop=TRUE)
  plot.reproducibility(sgRNA_reps[,c("Category",as.character(grp[[1]]))],names(grp)[1])
}
```

### Gene reproducibility in second condition
```{r reproducibility_4,eval=TRUE}
if(ncol(gene_reps_mat)>1) {
  annotation2 <- annotation1[annotation1$Condition==conditions[2],]
  grp <- split(annotation2$Sample,annotation2[c("Condition")],drop=TRUE)
  plot.reproducibility(gene_reps[,c("Category",as.character(grp[[1]]))],names(grp)[1])
}
```

# Category distributions

### Distributions at the sgRNA level
```{r folds_sgRNA,eval=TRUE}
dataset <- reshape2::melt(sgRNA_reps,id.vars=c("sgRNA","Gene","Category"),value.name="Value",variable.name="Sample")
dataset <- merge(dataset,annotation1)
plot.folds(dataset)
```

### Distributions at the gene level
```{r folds_gene,eval=TRUE}
dataset <- reshape2::melt(gene_reps,id.vars=c("Gene","Category"),value.name="Value",variable.name="Sample")
dataset <- merge(dataset,annotation1)
plot.folds(dataset)
```

